### 2013-06-24 trunk/network-science/paper.tex

Then we move on the dynamic centrality, by extending the often used model
for static network named Katz centrality\cite{katz1953new}, which is actually
a generalized version of eigenvalue centrality which estimate the influence
of a node in social networks by counting the total number of walks between a pair of
node. We try to combine the activity and the clasical centrality metric and
expect to define a new centrality model that is mode sensitive to immediate
effect.

@@

\item \textit{father}[$1\dots|V|$], an array exploited by the historicall
union-find algorithm\cite{tarjan1975efficiency} (a weakened model), which
will be discussed later. Each of the elements contains:
\begin{itemize}
\item $u$, the identity of $v_i$'s father node if $u>0$, otherwise $v_i$
is a root node, and $-u$ is the size of the tree.
\item $t$, the time when $u$ becomes non-zero.
\end{itemize}

@@

\begin{algorithm}[htbp]
\caption{\textsc{Modify Eta}($\eta'$)}
\label{alg-eta}
\textbf{Time Complexity:} $O(1)$\\
\textbf{Additional Space:} $O(1)$
\begin{algorithmic}[1]
\State $\eta\gets\eta'$;\State\Comment{Imcompatible with historical queries.
The alternative is to rebuild the whole graph.}
\end{algorithmic}
\end{algorithm}

\begin{algorithm}[htbp]
\caption{\textsc{Query Centrality}($t$,$\alpha$,$\beta$,
$\mathbf{x}_0$,$m$)}
\label{alg-cen}
\textbf{Time Complexity:} $O(mK|V|)$, $K$ is the sparsity constant.\\
\textbf{Additional Space:} $O(|V|)$
\begin{algorithmic}[1]
\Require $0<\alpha<\lambda_1(A^\bullet(G_t))^{-1}$ and $\beta>0$ and $m>0$. Here
$\lambda_1(A)$ is the maximal possitive eigenvalue of matrix $A$.
\Ensure return the active centrality $\mathbf{x}(G_t)$.
\For{$i\gets 1\dots|V|$}
\State $a[i]\gets \Call{Query Activity}{t,v_i}$;
\State $d[i]\gets \mathrm{size}(\mathit{edgeListReduced}[i])$;
\State $\mathbf{x}[i]\gets \mathbf{x}_0[i]$;
\EndFor
\For{$\mathit{count}\gets 1\dots m$}
\For{$i\gets 1\dots|V|$}
\State $\mathbf{x'}[i]\gets \beta$;
\EndFor
\For{$i\gets 1\dots|V|$}
\ForAll{$j\in\mathit{edgeListReduced}[i]$}
\State $\mathbf{x'}[i]\gets \mathbf{x'}[i]+\alpha\cdot
a[j]\cdot\mathbf{x}[j]/d[j]$
\EndFor\EndFor
\For{$i\gets 1\dots|V|$}
\State $\mathbf{x}[i]\gets \mathbf{x'}[i]$;
\EndFor
\EndFor
\State\Return{$\mathbf{x}$};
\end{algorithmic}
\end{algorithm}

@@

\section{Experiment}
\subsection{Data Generation} 
Our data generation is base on real social networks provided by \cite{database1,
database2}. Unfortunately, those databases do not contain evolving history
recorded data, so we simulate the evolving history by use the
authentic graph as the final state of the tested dynamic graph.
We give a random permutation to the edges, in a way such that:
\begin{itemize}
\item There will always
be just one component -- known as the giant component. We never add an edge out
of the giant component, so the evolving of the network seems to have increasing
vertices joining to the network.
\item The time delay of two adjacent new edges is inversely proportional to the
size of the giant component. So the average activity of any indivitual node do
not change tremendously.
\end{itemize}
Because the final state
is from real world data, it is ensured 
the evolving graph generated by our model will satisfy all the property that we
discussed in section 2.2. In addition, Kumar introduced how to generate
an artificial evolving social networks\cite{kumar2010structure}.

\subsection{Program}
We have implemented the algorithms using C++ language without compiler
optimization, and all execution is done under a typical PC with 
Intel (R) Core (TM) i3 CPU M380  @ 2.53GHz, 2GB RAM.

@@

The centrality trace graph for some representative node, when $\mu=4096$ and
$\eta=1000$:
\begin{center} \begin{tikzpicture}[y=.4cm, x=.5cm, font=\sffamily]
	\draw (0,0) -- coordinate (x axis mid) (21, 0);
	\draw (0,0) -- coordinate (y axis mid) (0, 11);
	\node[below=0.5cm] at (x axis mid) {\scriptsize Time ($\times10^3$)};
	\node[rotate=90, left=0.8cm] at (0, 10) {\scriptsize Magnitude of
	Centrality};
	\foreach \x in {1,2,...,20}
	\draw (\x,1pt) -- (\x,-3pt) node[anchor=north] {\scriptsize \x};
		\foreach \y in {1,2,...,11}
		\draw (1pt,\y) -- (-3pt,\y) node[anchor=east] {\scriptsize \y};
	\draw[color=red!70!black,line width=1pt] plot file {exp-g3-1};
	\draw[color=blue!70!black] plot file {exp-g3-2};
	\begin{scope}[shift={(2,8)}]
	\draw[color=red!70!black,line width=1pt] (0,0) -- (2,0)
		node[right]{\scriptsize evolving centrality};
	\draw[color=blue!50!black] (0,1) -- (2,1)
		node[right]{\scriptsize static centrality};
	\end{scope}
\end{tikzpicture} \end{center}

\begin{center} \begin{tikzpicture}[y=.4cm, x=.5cm, font=\sffamily]
	\draw (0,0) -- coordinate (x axis mid) (21, 0);
	\draw (0,0) -- coordinate (y axis mid) (0, 11);
	\node[below=0.5cm] at (x axis mid) {\scriptsize Time ($\times10^3$)};
	\node[rotate=90, left=0.8cm] at (0, 10) {\scriptsize Magnitude of
	Centrality};
	\foreach \x in {1,2,...,20}
	\draw (\x,1pt) -- (\x,-3pt) node[anchor=north] {\scriptsize \x};
		\foreach \y in {1,2,...,11}
		\draw (1pt,\y) -- (-3pt,\y) node[anchor=east] {\scriptsize \y};
	\draw[color=red!70!black,line width=1pt] plot file {exp-g9-1};
	\draw[color=blue!70!black] plot file {exp-g9-2};
	\begin{scope}[shift={(2,8)}]
	\draw[color=red!70!black,line width=1pt] (0,0) -- (2,0)
		node[right]{\scriptsize evolving centrality};
	\draw[color=blue!50!black] (0,1) -- (2,1)
		node[right]{\scriptsize static centrality};
	\end{scope}
\end{tikzpicture} \end{center}

The centrality trace graph for some representative node, when $\mu=2^{20}$ and
$\eta=2000$:
\begin{center} \begin{tikzpicture}[y=.4cm, x=.5cm, font=\sffamily]
	\draw (0,0) -- coordinate (x axis mid) (21, 0);
	\draw (0,0) -- coordinate (y axis mid) (0, 11);
	\node[below=0.5cm] at (x axis mid) {\scriptsize Time ($\times10^3$)};
	\node[rotate=90, left=0.8cm] at (0, 10) {\scriptsize Magnitude of
	Centrality};
	\foreach \x in {1,2,...,20}
	\draw (\x,1pt) -- (\x,-3pt) node[anchor=north] {\scriptsize \x};
		\foreach \y in {1,2,...,11}
		\draw (1pt,\y) -- (-3pt,\y) node[anchor=east] {\scriptsize \y};
	\draw[color=red!70!black,line width=1pt] plot file {exp-g8-1};
	\draw[color=blue!70!black] plot file {exp-g8-2};
	\begin{scope}[shift={(2,8)}]
	\draw[color=red!70!black,line width=1pt] (0,0) -- (2,0)
		node[right]{\scriptsize evolving centrality};
	\draw[color=blue!50!black] (0,1) -- (2,1)
		node[right]{\scriptsize static centrality};
	\end{scope}
\end{tikzpicture} \end{center}
\begin{center} \begin{tikzpicture}[y=.4cm, x=.5cm, font=\sffamily]
	\draw (0,0) -- coordinate (x axis mid) (21, 0);
	\draw (0,0) -- coordinate (y axis mid) (0, 11);
	\node[below=0.5cm] at (x axis mid) {\scriptsize Time ($\times10^3$)};
	\node[rotate=90, left=0.8cm] at (0, 10) {\scriptsize Magnitude of
	Centrality};
	\foreach \x in {1,2,...,20}
	\draw (\x,1pt) -- (\x,-3pt) node[anchor=north] {\scriptsize \x};
		\foreach \y in {1,2,...,11}
		\draw (1pt,\y) -- (-3pt,\y) node[anchor=east] {\scriptsize \y};
	\draw[color=red!70!black,line width=1pt] plot file {exp-g11-1};
	\draw[color=blue!70!black] plot file {exp-g11-2};
	\begin{scope}[shift={(2,8)}]
	\draw[color=red!70!black,line width=1pt] (0,0) -- (2,0)
		node[right]{\scriptsize evolving centrality};
	\draw[color=blue!50!black] (0,1) -- (2,1)
		node[right]{\scriptsize static centrality};
	\end{scope}
\end{tikzpicture} \end{center}

@@

By the final experiment, we can observe that the increase on magnitude of
evolving centrality is similar to that of the static one. However, when the
influence of a node stops increase so fast, our evolving centrality quickly
pulls back, while the static centrality usually keeps a high value for long
time. In many fields, the social concern are supposed to be sensitive to time
, innovation and activeness, instead of imposing more attention to historical
issues that are once very popular. Those fields such as web-page search
engine[?], ranking of movie actors[?], seeking hot scholar topics, etc.
By using evolving centrality, the increment of actions of a node and its
closely related region will be more notable in increment of its ranking of
influence, whereas the static centrality is more likely to trigger cascade on
social preference[?] because people will have less chance to see and rate new
information. The cascade may prevent high quality information from being
popular, and even worse, hasten the monopolization in the commercial aspect.

>>>>

Then we move on the dynamic centrality, by extending the often used model
for static network named Katz centrality\cite{katz1953new}, which is actually
a generalized version of eigenvalue centrality which estimate the influence
of a node in social networks by counting the total number of walks between a pair of
node. We try to combine the activity and the classical centrality metric and
expect to define a new centrality model that is more sensitive to immediate
effect.

@@

\item \textit{father}[$1\dots|V|$], an array exploited by the historical
union-find algorithm\cite{tarjan1975efficiency} (a weakened model), which
will be discussed later. Each of the elements contains:
\begin{itemize}
\item $u$, the identity of $v_i$'s father node if $u>0$, otherwise $v_i$
is a root node, and $(-u)$ is the size of the tree.
\item $t$, the time when $u$ becomes non-zero.
\end{itemize}

@@

\begin{algorithm}[htbp]
\caption{\textsc{Modify Eta}($\eta'$)}
\label{alg-eta}
\textbf{Time Complexity:} $O(1)$\\
\textbf{Additional Space:} $O(1)$
\begin{algorithmic}[1]
\State $\eta\gets\eta'$;\State\Comment{Incompatible with historical queries.
The alternative is to rebuild the whole graph.}
\end{algorithmic}
\end{algorithm}

\begin{algorithm}[htbp]
\caption{\textsc{Query Centrality}($t$,$\alpha$,$\beta$,
$\mathbf{x}_0$,$m$)}
\label{alg-cen}
\textbf{Time Complexity:} $O(mK|V|)$, $K$ is the sparsity constant.\\
\textbf{Additional Space:} $O(|V|)$
\begin{algorithmic}[1]
\Require $0<\alpha<\lambda_1(A^\bullet(G_t))^{-1}$ and $\beta>0$ and $m>0$. Here
$\lambda_1(A)$ is the maximal positive eigenvalue of matrix $A$.
\Ensure return the active centrality $\mathbf{x}(G_t)$.
\For{$i\gets 1\dots|V|$}
\State $a[i]\gets \Call{Query Activity}{t,v_i}$;
\State $k[i]\gets \mathrm{size}(\mathit{edgeListReduced}[i])$;
\State $\mathbf{x}[i]\gets \mathbf{x}_0[i]$;
\EndFor
\For{$\mathit{count}\gets 1\dots m$}
\For{$i\gets 1\dots|V|$}
\State $\mathbf{x'}[i]\gets \beta$;
\EndFor
\For{$i\gets 1\dots|V|$}
\ForAll{$j\in\mathit{edgeListReduced}[i]$}
\State $\mathbf{x'}[i]\gets \mathbf{x'}[i]+\alpha\cdot
a[j]\cdot\mathbf{x}[j]/k[j]$
\EndFor\EndFor
\For{$i\gets 1\dots|V|$}
\State $\mathbf{x}[i]\gets \mathbf{x'}[i]$;
\EndFor
\EndFor
\State\Return{$\mathbf{x}$};
\end{algorithmic}
\end{algorithm}

@@

\section{Experiment}
\subsection{Data Generation} 
Our data generation is base on real social networks provided by \cite{database1,
database2}. Unfortunately, those databases do not contain evolving history
recorded data, so we simulate the evolving history by use the
authentic graph as the final state of the tested dynamic graph.
We give a random permutation to the edges, in a way such that:
\begin{itemize}
\item There will always
be just one component -- known as the giant component. We never add an edge out
of the giant component, so the evolving of the network seems to have increasing
vertices joining to the network.
\item The time delay of two adjacent new edges is inversely proportional to the
size of the giant component. So the average activity of any individual node
would not change tremendously.
\end{itemize}
Because the final state
is from real world data, it is ensured 
the evolving graph generated by our model will satisfy all the property that we
discussed in section 2.2. In addition, Kumar introduced how to generate
an artificial evolving social networks\cite{kumar2010structure}.

\subsection{Program}
We have implemented the algorithms using C++ language without compiler
optimization, and all executions are done under a typical PC with 
Intel (R) Core (TM) i3 CPU M380  @ 2.53GHz, 2GB RAM.

@@

\begin{itemize}
\item The centrality trace graph for some representative node, when $\mu=4096$ and
$\eta=1000$:
\begin{center} \begin{tikzpicture}[y=.4cm, x=.5cm, font=\sffamily]
	\draw (0,0) -- coordinate (x axis mid) (21, 0);
	\draw (0,0) -- coordinate (y axis mid) (0, 11);
	\node[below=0.5cm] at (x axis mid) {\scriptsize Time ($\times10^3$)};
	\node[rotate=90, left=0.8cm] at (0, 10) {\scriptsize Magnitude of
	Centrality};
	\foreach \x in {1,2,...,20}
	\draw (\x,1pt) -- (\x,-3pt) node[anchor=north] {\scriptsize \x};
		\foreach \y in {1,2,...,11}
		\draw (1pt,\y) -- (-3pt,\y) node[anchor=east] {\scriptsize \y};
	\draw[color=red!70!black,line width=1pt] plot file {exp-g3-1};
	\draw[color=blue!70!black] plot file {exp-g3-2};
	\begin{scope}[shift={(2,8)}]
	\draw[color=red!70!black,line width=1pt] (0,0) -- (2,0)
		node[right]{\scriptsize evolving centrality};
	\draw[color=blue!50!black] (0,1) -- (2,1)
		node[right]{\scriptsize static centrality};
	\end{scope}
\end{tikzpicture} \end{center}
Evolving centrality is smaller then static one, because we applied the
activity coefficients which is less than $1$. The overall tendency of those
traces are similar, but the evolving centrality declines more quickly.
\begin{center} \begin{tikzpicture}[y=.4cm, x=.5cm, font=\sffamily]
	\draw (0,0) -- coordinate (x axis mid) (21, 0);
	\draw (0,0) -- coordinate (y axis mid) (0, 11);
	\node[below=0.5cm] at (x axis mid) {\scriptsize Time ($\times10^3$)};
	\node[rotate=90, left=0.8cm] at (0, 10) {\scriptsize Magnitude of
	Centrality};
	\foreach \x in {1,2,...,20}
	\draw (\x,1pt) -- (\x,-3pt) node[anchor=north] {\scriptsize \x};
		\foreach \y in {1,2,...,11}
		\draw (1pt,\y) -- (-3pt,\y) node[anchor=east] {\scriptsize \y};
	\draw[color=red!70!black,line width=1pt] plot file {exp-g9-1};
	\draw[color=blue!70!black] plot file {exp-g9-2};
	\begin{scope}[shift={(2,8)}]
	\draw[color=red!70!black,line width=1pt] (0,0) -- (2,0)
		node[right]{\scriptsize evolving centrality};
	\draw[color=blue!50!black] (0,1) -- (2,1)
		node[right]{\scriptsize static centrality};
	\end{scope}
\end{tikzpicture} \end{center}
We can observe that two centralities can react quite differently to changes.

\item The centrality trace graph for some representative node, when $\mu=2^{20}$ and
$\eta=2000$:
\begin{center} \begin{tikzpicture}[y=.4cm, x=.5cm, font=\sffamily]
	\draw (0,0) -- coordinate (x axis mid) (21, 0);
	\draw (0,0) -- coordinate (y axis mid) (0, 11);
	\node[below=0.5cm] at (x axis mid) {\scriptsize Time ($\times10^3$)};
	\node[rotate=90, left=0.8cm] at (0, 10) {\scriptsize Magnitude of
	Centrality};
	\foreach \x in {1,2,...,20}
	\draw (\x,1pt) -- (\x,-3pt) node[anchor=north] {\scriptsize \x};
		\foreach \y in {1,2,...,11}
		\draw (1pt,\y) -- (-3pt,\y) node[anchor=east] {\scriptsize \y};
	\draw[color=red!70!black,line width=1pt] plot file {exp-g8-1};
	\draw[color=blue!70!black] plot file {exp-g8-2};
	\begin{scope}[shift={(2,8)}]
	\draw[color=red!70!black,line width=1pt] (0,0) -- (2,0)
		node[right]{\scriptsize evolving centrality};
	\draw[color=blue!50!black] (0,1) -- (2,1)
		node[right]{\scriptsize static centrality};
	\end{scope}
\end{tikzpicture} \end{center}
By elongating the activity delay, the declination becomes slower for evolving
centrality. However, it still declines faster than the static one.
\begin{center} \begin{tikzpicture}[y=.4cm, x=.5cm, font=\sffamily]
	\draw (0,0) -- coordinate (x axis mid) (21, 0);
	\draw (0,0) -- coordinate (y axis mid) (0, 11);
	\node[below=0.5cm] at (x axis mid) {\scriptsize Time ($\times10^3$)};
	\node[rotate=90, left=0.8cm] at (0, 10) {\scriptsize Magnitude of
	Centrality};
	\foreach \x in {1,2,...,20}
	\draw (\x,1pt) -- (\x,-3pt) node[anchor=north] {\scriptsize \x};
		\foreach \y in {1,2,...,11}
		\draw (1pt,\y) -- (-3pt,\y) node[anchor=east] {\scriptsize \y};
	\draw[color=red!70!black,line width=1pt] plot file {exp-g11-1};
	\draw[color=blue!70!black] plot file {exp-g11-2};
	\begin{scope}[shift={(2,8)}]
	\draw[color=red!70!black,line width=1pt] (0,0) -- (2,0)
		node[right]{\scriptsize evolving centrality};
	\draw[color=blue!50!black] (0,1) -- (2,1)
		node[right]{\scriptsize static centrality};
	\end{scope}
\end{tikzpicture} \end{center}
We observe a clear concave in evolving centrality from time $12\,000$ to
$16\,000$. Perhaps the reason for that is the neighbors of the vertex becomes
less active, despite the static structural centrality is high.
\end{itemize}

@@

By the final experiment, we can observe that the increase on magnitude of
evolving centrality is similar to that of the static one. However, when the
influence of a node stops increase so fast, our evolving centrality quickly
pulls back, while the static centrality usually keeps a high value for long
time. In many fields, the social concern are supposed to be sensitive to time
, innovation and activeness, instead of imposing more attention to historical
issues that are once very popular. Those fields such as web-page search
engine, ranking of movie actors, seeking hot scholar topics, etc.
By using evolving centrality, the increment of actions of a node and its
closely related region will be more notable in increment of its ranking of
influence, whereas the static centrality is more likely to trigger
conformity on social preference\cite{cialdini2004social} because people will
have less chance to see and rate new information, which may prevent high
quality information from getting popular, and even worse, hasten the
monopolization in the commercial
aspect.
